Embeddings and Attention in Predictive Modeling

### 2021-04-08 manuscript/manuscript.Rmd
final edits

---
title: Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevinykuo@gmail.com 
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants and University of the Witwatersrand
    email: ron@ronaldrichman.co.za
abstract: |
  Categorical data are ubiquitous in insurance modeling. In this paper, we explore in depth how these data can be
  processed with categorical embeddings in the context of claim severity modeling. We develop several models that range
  in complexity from simple neural networks to state-of-the-art attention based architectures and calibrate categorical
  embeddings using these models. We illustrate the utility of these learned embeddings as pretrained features in a
  generalized linear model. We discuss methods for visualizing and interpreting learned embeddings. Finally, we explore
  how attention based models can contextually augment embeddings, leading to enhanced predictive performance.
keywords:
  - categorical data
  - neural networks
  - embeddings
  - attention
  - severity modeling
  - National Flood Insurance Program 
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
header-includes: |
    \usepackage{amsmath}
    \usepackage{mathtools}
    \usepackage{bm}
    \usepackage{bbm}
    \usepackage{float}
    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
    \newcommand{\norm}[1]{\| #1 \|}
---

@@

The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except that a more specialized form of self-attention is used to select the most important covariates for the modeling problem.

>>>>

---
title: Embeddings and Attention in Predictive Modeling 
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevinykuo@gmail.com 
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants and University of the Witwatersrand
    email: ron@ronaldrichman.co.za
abstract: |
  We explore in depth how categorical data can be
  processed with embeddings in the context of claim severity modeling. We develop several models that range
  in complexity from simple neural networks to state-of-the-art attention based architectures that utilize embeddings. 
  We illustrate the utility of learned embeddings from neural networks as pretrained features in
  generalized linear models, and discuss methods for visualizing and interpreting embeddings. Finally, we explore
  how attention based models can contextually augment embeddings, leading to enhanced predictive performance.
keywords:
  - categorical data
  - neural networks
  - embeddings
  - attention
  - severity modeling
  - National Flood Insurance Program 
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
header-includes: |
    \usepackage{amsmath}
    \usepackage{mathtools}
    \usepackage{bm}
    \usepackage{bbm}
    \usepackage{float}
    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
    \newcommand{\norm}[1]{\| #1 \|}
---

@@

The final model we consider in this subsection is the TabNet architecture. In TabNet, similar to decision trees which 
it is inspired by, the input features are processed
sequentually in a number of decision steps. In each decision step, a different subset of features are weighted more
than the rest based on masks defined by attention modules applied to information from the previous step. The output
of each step consists of information for the next decision step, and also an output representation that is set aside 
then aggregated at the end, along with other decision step outputs, in order to product the final model output.
Due to the complexity, we refer the reader to @Ark2019 for the full architectural details.
